%\documentclass[aps,prl,showpacs,superscriptaddress,amsmath,amssymb,obeyspaces]{revtex4}

\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}% Include figure files
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{booktabs}
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}


 \definecolor{darkgreen}{rgb}{0.3,0.5,0.3}
 \definecolor{darkblue}{rgb}{0.3,0.3,0.5}
 \definecolor{darkred}{rgb}{0.5,0.3,0.3}
 \lstdefinelanguage{LUA}{%
  sensitive=true,%
  columns=fixed,%
  keywordstyle=[1]{\color{darkblue}\bfseries},%
  keywordstyle=[2]{\color{darkgreen}\bfseries},%
  morekeywords=[1]{local,if,then,else,end,while,do, coroutine,yield},% Official LUA keywords
  morekeywords=[2]{SMA_Handle, Controller, handle, Output, FindFile},% Your private keywords
  otherkeywords={.,=,~,*,>,:},%
  morestring=[b]",%
  stringstyle={\color{darkred}\itshape},%
  breaklines=true,%
  linewidth=\textwidth,%
  comment=[l]{--}%
 }



\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  emph = {force, Force, Integrator},      % ProtoMol conf keyword
  emphstyle = {\bfseries}, % Keyword style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8 
 frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=bash,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=10,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}
\usepackage{courier}

\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
%\lstset{framextopmargin=50pt,frame=bottomline}

\begin{document}
\begin{section} {Introduction}
 According to its website, \textsc{ProtoMol} is an ``object-oriented, component based, framework for molecular dynamics (MD) simulations''. It was first developed in 2004 and its most recent version is v3.0. Written in \textsc{C++},  \textsc{ProtoMol} can simulate common classical mechanics with very high efficiency. Although it was designed originally for chemistry/biochemistry simulation, it has been succesfully adapted to simulate ion trap dynamics. For a detailed review of \textsc{ProtoMol}, please see Ref. 
\end{section}
{section} {Obtaining \textsc{ProtoMol}}
\textsc{ProtoMol} is open-source and cross platform. The source code of \textsc{ProtoMol} is hosted at \textsc{sourceforge}, and the download URL is \url{http://sourceforge.net/projects/protomol/files/ProtoMol/Protomol 3.3/} for each platform. The Linux version used in Hudson lab simulations has undergone considerable modification, so I highly recommend downloading the modified version to start with. The address is \url{https://github.com/kuangchen/ProtoMol}. Any \textsc{git} tool should be able to clone this online repository into local copies.

\end{section}
\include{compile}
\include{basic_usage}
\begin{section} {Using the ProtoMol Addons}
Although \textsc{ProtoMol} is a powerful MD simulation software, it does not meet every specific simulation goals right out of box. Modification and extension of the source codes are needed, to achieve these goals. In this section, I will present the usage of the extensions I wrote in particular for the ion trap simulation.

\begin{subsection} {Force from the trapping field}
To define the force from the trapping rf-field, the following force specification should be added to the integrator. 
\begin{lstlisting}[language=bash]
force LQT 
-lqt_filename trap.lua
\end{lstlisting}
filename specifies the filename of trap definition, which is written in the language of Lua. An example file of trapp definition file is given below,
\begin{lstlisting}[language=LUA]{Example trap definition file}
trap = { m = 173, -- AMU
  r0 = 12e-3,     -- m
  z0 = 21.5e-3,   -- m
  v_rf = 175/2,   -- V
  v_ec = 10,      -- V
  eta = 0.1275,   -- 1
  omega = 300e3   -- Hz
}
\end{lstlisting}
The trap definition declares a variable trap, a Lua table that defines an ion trap through its fields. The meaning of each field is given by Eq. \footnote{The ion is assumed to be singly charged. For multiply-charged ion, ion's mass needs to be scaled accordingly.}. The unit of each quantity is given in the comment. 
\end{subsection}

\begin{subsection} {Harmonic trap force}
If one is not concerned about rf-heating, one can use the pondermotive potential to approximate the real trap potential. 
\begin{lstlisting}[language=bash]
force HarmonicTrapForce
-ht_def ht_trap.lua
\end{lstlisting}
where -ht\_def points to a lua file that defines the trapping frequency.
\begin{lstlisting}[language=LUA]{Example trap definition file}
trap = { freq = { x = 39.63e3 * 2 * 3.14159,
                  y = 39.63e3 * 2 * 3.14159,
                  z = 39.63e3 * 2 * 3.14159 } }
\end{lstlisting}
The trap definition declares a variable trap, a Lua table that contains a single field freq, which in turn contains three field x, y, z. The meanings and units of these field are given in the following table.
\begin{table}[h!]
  \centering
  \begin{tabular}{ c  c  l } \toprule
    Field & Unit & Meaning\\ \midrule
    $\omega_x$ & Hz & trapping frequency defined by $V=\frac{1}{2}(\omega_x^2x^2+\omega_y^2y^2+\omega_z^2z^2)$\\
    $\omega_y$ & Hz &   \\
    $\omega_z$ & Hz &   \\ \bottomrule
  \end{tabular}
  \caption{Damping Force Definition File}
  \label{tab:harmonic_trap_def}
\end{table}


\end{subsection}
\begin{subsection} {Damping force}
The damping force is introduced to emulate the laser-cooling force, which quickly removes ions' kinetic energy, and cause the ions to form Coulomb crystal. The damping force is added to the simulation by
\begin{lstlisting}
force DampingForce
-damping_def damping.lua
\end{lstlisting}
where -damping\_def points to a lua file that defines the damping coefficient, and the duration when the damping is on.
\begin{lstlisting}[language=LUA]{Example trap definition file}
  damping = { coeff = 3e-22,
    t_start = -1,
    t_end = 0.01 }
\end{lstlisting}


\begin{table}[h!]
  \centering
  \begin{tabular}{ c  c  l } \toprule
    Field & Unit & Meaning\\ \midrule
    coeff & ? & damping coeffient $b$, defined by $\mathbf{F}=-b\mathbf{v}$\\
    t\_start & sec & start time  \\
    t\_end & sec & end time  \\ \bottomrule
  \end{tabular}
  \caption{Damping Force Definition File}
  \label{tab:damping_def}
\end{table}

\end{subsection}

\begin{subsection} {Leap Frog Buffer Gas Integrator V2}
To introduce collisions with ultracold neutral atoms, a leap frog integrator is written. An example input is given by
\begin{lstlisting}
level X LeapFrogBufferGas2 {
  timestep 1e8
  filename buffer_gas.lua
}
\end{lstlisting}
where buffer\_gas\_def points to the buffer gas definition file.
\begin{lstlisting}[language=LUA]{Example trap buffer_gas file}
  neutral = { mass = 40,
    polarizability = 50,
    temperature = 5e-3,
    density = 1e16 }

  trap = { radius = 12e-3, 
    z0 = 21.5e-3 }
\end{lstlisting}


\begin{table}[h!]
  \centering
  \begin{tabular}{ c  c  l } \toprule
    Field & Unit & Meaning\\ \midrule
    mass & AMU & mass of neutral atom \\
    polarizability & $10^{24} cm^3$ & polarizability of neutral atom \\
    temperature & Kelvin & temperature of neutral atom \\
    density & $m^3$ & density of neutral atom
  \end{tabular}
  \caption{Buffer Gas Definition Part I}
  \label{tab:leapfrogintegrator_def_p1}
\end{table}

\begin{table}[h!]
  \centering
  \begin{tabular}{ c  c  l } \toprule
    Field & Unit & Meaning\\ \midrule
    radius & $m$ & radius of ion trap \\
    polarizability & $10^{24} cm^3$ & polarizability of neutral atom \\
    temperature & Kelvin & temperature of neutral atom \\
    density & $m^3$ & density of neutral atom
  \end{tabular}
  \caption{Buffer Gas Definition Part II}
  \label{tab:leapfrogintegrator_def_p2}
\end{table}
\end{subsection}

\end{section}
\include{ion_snapshot}
\begin{section} {Writing your own \textsc{ProtoMol} extensions}
\begin{subsection} {Adding a new force}
  
\end{subsection}

\begin{subsection} {Adding a new integrator}
  
\end{subsection}

\begin{subsection} {Adding a new output}
  
\end{subsection}



\end{section}
\end{document}
 
%  LocalWords:  overline
